Tables/Graphs for Article

### 2018-01-14 article/draft1.tex
reformated tables of splines and final model results, changed rounding in table of metrics

\section*{Abstract} % fix the hazard ratios!!!!

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question receives it's first response. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR...), factors related to the question's title (e.g., whether or not it was phrased as a question (HR..)), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR..)). Future studies can investigate whether factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

% % Univariate analysis results
% \begin{table}[!htbp]
% \centering
% \begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
%   \hline
%   \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
%   \hline \hline
%   \multirow{ 3 }{ 5cm }{ Average tag frequency }
%   & Untransformed & 1.270620e-08 \\
%   & Log + 1 & 1.186521e-08 \\
%   & \textbf{*}Square root & 1.464184e-11 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Average tag length }
%   & Untransformed & 2.611529e-02 \\ 
%   & \textbf{*}Log + 1 & 6.018542e-05 \\
%   & Square root & 2.999917e-04 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Device name length }
%   & Untransformed & 6.530431e-03 \\
%   & \textbf{*}Log + 1 & 1.912977e-05 \\
%   & Square root & 2.291424e-04 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
%   & Untransformed & 1.398819e-07 \\
%   & Log + 1 & 1.092952e-07 \\
%   & \textbf{*}Square root & 1.148792e-11 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Text length }
%   & Untransformed & 6.947221e-12 \\
%   & \textbf{*}Log & 0.000000e+00 \\
%   & Square root & 1.110223e-16 \\ \hline \hline
%   \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
%   \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
% \end{tabular}
% \caption{Univariate analysis results} 
% \label{table:univariate_results}
% \end{table}

Each training set contained 6,208 questions, and each test set contained 1,552 questions. Univariate analysis performed on one training set indicated that all cateogorical predictors were signficant with partial likelihood ratio p-values of less than 0.001. All continuous predictors, except for device length and average tag length, also resulted in univariate p-values of less than 0.001. Applying either square root or log transformations to continuous variables resulted in univariate p-values of less than 0.001. For continuous predictors that contained zeros, one was added to each observation before applying the log transformation. The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus 1 transformation of average tag length, log plus 1 transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length. All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.

% Splines
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{5cm} | l | l |}
  \hline
  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
  \hline
  \multirow{ 4 }{ 5cm }{ Log transformation of text length } 
  & 0 & 65862.83 \\ 
  & \textbf{*}5 & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of line breaks to text length ratio }
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & \textbf{*}3 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average tag frequency }
  & \textbf{*}0 & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of device name length + 1 }
  & 0 & 65918.06 \\ 
  & \textbf{*}5 & 65847.34 \\ 
  & 4 & 65880.89 \\ 
  & 3 & 65898.00 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of average tag length + 1 }
  & 0 & 65920.24 \\ 
  & 5 & 65911.20 \\ 
  & \textbf{*}4 & 65910.81 \\ 
  & 3 & 65914.98 \\ 
   \hline
\end{tabular}
\caption{Determining the optimal k number of splines for each predictor} 
\label{table:splines}
\end{table}

@@

\begin{table}[!htbp]
\centering
\begin{tabular}{|L{7cm}|L{7cm}|}
\hline
\textbf{Device} & iPhone 6 \\ \hline
\textbf{Title} & iPhone water damage, touch screen issue \\ \hline
\textbf{Text} & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? \\ \hline
\textbf{Tags} & touchscreen, water damage \\ \hline
\textbf{Response Time (hrs)} & 1.361 \\ \hline 
\textbf{Device Category} & Apple Product \\ \hline
\textbf{Day Posted} & Weekday \\ \hline
\textbf{Text length (characters)} & 241 \\ \hline
\textbf{Device name length (characters)} & 8 \\ \hline
\textbf{Average tag length (characters)} & 11.5 \\ \hline
\textbf{Title end in a question mark?} & False \\ \hline
\textbf{Text in all lower case?} & False \\ \hline
\textbf{Text contain end punctuation?} & True \\ \hline
\textbf{User update question after posting?} & False \\ \hline
\textbf{User indicate prior effort?} & False \\ \hline
\textbf{Line break to text length ratio} & 0 \\ \hline
\textbf{Average tag frequency} & 0.0097 \\ \hline
\textbf{Frequently-used answered words?} & True \\ \hline
\textbf{Frequently-used unanswered words?} & False \\ \hline \hline
% next question
\textbf{Device} & android tablet \\ \hline
\textbf{Title} & ccccaaaan you help me fix my touch screen \\ \hline
\textbf{Text} & touch screen not worki \\ \hline
\textbf{Tags} & NA \\ \hline
\textbf{Response Time (hrs)} & NA \\ \hline 
\textbf{Device Category} & Tablet \\ \hline
\textbf{Day Posted} & Weekday \\ \hline
\textbf{Text length (characters)} & 81 \\ \hline
\textbf{Device name length (characters)} & 18 \\ \hline
\textbf{Average tag length (characters)} & 47 \\ \hline
\textbf{Title end in a question mark?} & False \\ \hline
\textbf{Text in all lower case?} & True \\ \hline
\textbf{Text contain end punctuation?} & False \\ \hline
\textbf{User update question after posting?} & False \\ \hline
\textbf{User indicate prior effort?} & False \\ \hline
\textbf{Line break to text length ratio} & 0 \\ \hline
\textbf{Average tag frequency} & 0 \\ \hline
\textbf{Frequently-used answered words?} & True \\ \hline
\textbf{Frequently-used unanswered words?} & True \\ \hline \hline
\end{tabular}
\caption{Answered and Unanswered questions}
\label{table:questions}
\end{table}

>>>>

\section*{Abstract}

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question receives it's first response. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

Each training set contained 6,208 questions. Each test set contained 1,552 questions. Univariate analysis performed on one training set indicated that all categorical predictors were signficant with partial likelihood ratio p-values of less than 0.001. Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001. Applying either square root or log transformations resulted in univariate p-values of less than 0.001. For those that contained zeros, one was added to each observation before applying the log transformation. The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus 1 transformation of average tag length, log plus 1 transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length. All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.

% Splines
\begin{table}[!htbp]
\centering
\begin{tabular}{| L{5cm} | l | l |}
  \hline
  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average tag frequency }
  & \textbf{*}0 & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of average tag length + 1 }
  & 0 & 65920.24 \\ 
  & 5 & 65911.20 \\ 
  & \textbf{*}4 & 65910.81 \\ 
  & 3 & 65914.98 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of device name length + 1 }
  & 0 & 65918.06 \\ 
  & \textbf{*}5 & 65847.34 \\ 
  & 4 & 65880.89 \\ 
  & 3 & 65898.00 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of line breaks to text length ratio }
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & \textbf{*}3 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5cm }{ Log transformation of text length } 
  & 0 & 65862.83 \\ 
  & \textbf{*}5 & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
\end{tabular}
\caption{Determining the optimal k number of splines for each continuous predictor} 
\label{table:splines}
\end{table}

@@

\begin{table}[!htbp]
\centering
\begin{tabular}{|L{7cm}|L{7cm}|}
\hline
\textbf{Device} & iPhone 6 \\ \hline
\textbf{Title} & iPhone water damage, touch screen issue \\ \hline
\textbf{Text} & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? \\ \hline
\textbf{Tags} & touchscreen, water damage \\ \hline
\textbf{Response Time (hrs)} & 1.361 \\ \hline 
\textbf{Device Category} & Apple Product \\ \hline
\textbf{Day Posted} & Weekday \\ \hline
\textbf{Text length (characters)} & 241 \\ \hline
\textbf{Device name length (characters)} & 8 \\ \hline
\textbf{Average tag length (characters)} & 11.5 \\ \hline
\textbf{Title end in a question mark?} & False \\ \hline
\textbf{Text in all lower case?} & False \\ \hline
\textbf{Text contain end punctuation?} & True \\ \hline
\textbf{User update question after posting?} & False \\ \hline
\textbf{User indicate prior effort?} & False \\ \hline
\textbf{Line break to text length ratio} & 0 \\ \hline
\textbf{Average tag frequency} & 0.0097 \\ \hline
\textbf{Frequently-used answered words?} & True \\ \hline
\textbf{Frequently-used unanswered words?} & False \\ \hline \hline
% next question
\textbf{Device} & android tablet \\ \hline
\textbf{Title} & ccccaaaan you help me fix my touch screen \\ \hline
\textbf{Text} & touch screen not worki \\ \hline
\textbf{Tags} & NA \\ \hline
\textbf{Response Time (hrs)} & NA \\ \hline 
\textbf{Device Category} & Tablet \\ \hline
\textbf{Day Posted} & Weekday \\ \hline
\textbf{Text length (characters)} & 81 \\ \hline
\textbf{Device name length (characters)} & 18 \\ \hline
\textbf{Average tag length (characters)} & 47 \\ \hline
\textbf{Title end in a question mark?} & False \\ \hline
\textbf{Text in all lower case?} & True \\ \hline
\textbf{Text contain end punctuation?} & False \\ \hline
\textbf{User update question after posting?} & False \\ \hline
\textbf{User indicate prior effort?} & False \\ \hline
\textbf{Line break to text length ratio} & 0 \\ \hline
\textbf{Average tag frequency} & 0 \\ \hline
\textbf{Frequently-used answered words?} & True \\ \hline
\textbf{Frequently-used unanswered words?} & True \\ \hline
\end{tabular}
\caption{Answered and unanswered questions}
\label{table:questions}
\end{table}
